### 2024-08-07 manuscript.tex
Figure improvements

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{img/cloud_occurrence_agg.pdf}
\caption{
Cloud occurrence by height aggregated from the 31 voyages and one station for
observations (OBS), the ICON model, and the MERRA-2 and ERA5 reanalyses. The
total cloud fraction (CF) is shown in the legend. The ranges are from the
16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile. \textbf{(a)} all conditions,
\textbf{(b)}, \textbf{(c)} cyclonic and non-cyclonic conditions as identified
by cyclone tracking, \textbf{(d)}, \textbf{(e)} stable and unstable conditions
as divided by the lower tropospheric stability criterion.
}
\label{fig:cloud-occurrence}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/clt_hist.pdf}
\caption{
Daily total cloud fraction histograms calculated as the average of all voyage
and station histograms. The models and subsets are as in Fig.
\ref{fig:cloud-occurrence}
}
\label{fig:clt-hist}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{img/cloud_occurrence_agg.pdf}
\caption{
Cloud occurrence by height calculated as the average of all voyages and stations
for the observed (OBS) and simulated lidar cloud mask. The total cloud fraction
(CF), average shortwave (SW) and longwave (LW) are shown in the legend. The
bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from
the set of all voyages and stations. The subsets \textbf{(a--g)} are described
in the text (Section \ref{sec:results}).}
\label{fig:cloud-occurrence}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/clt_hist.pdf}
\caption{
Daily total cloud fraction histograms calculated as the average of all voyage
and station histograms. The total cloud fraction of a day (UTC) is calculated
as a fraction of cloudy (based on the cloud mask) observed (OBS) or simulated
lidar profiles. The models and subsets are as in Fig.
\ref{fig:cloud-occurrence}.
}
\label{fig:clt-hist}
\end{figure}
